Meta-analysis

### 2020-06-18 04_MetaAnalysis.Rmd
Change the mean square error to sampling variance calculation till the formula can be verified.
Edit explaination -still needs editing

@@

```{r MSE_2_SVar}
slimmer_PM_dat$vi <-
   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
                                  2)
```

@@

   # First we neee to Calculate the pooled standard deviation
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <- 
   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"vi"])/
           (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))

@@

Lets undertake the meta-analysis, we are using the `spray_management` variable as a moderator and a interactive term to the `trial` variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management -1,
   method = "ML",
   random = ~ spray_management|trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero. 
However the other treatments are significantly different to zero.
the Qm omnibus test of moderators show the moderators significantly influence the model and we can reject the null hypothesis that there is no difference between the moderators. 
The Qe test shoes there is a large significant amount of residual Heterogeneity.

@@

#### CONTINUE FROM HERE!!!!!!!!!!

@@

PM_mv_AI2 <- rma.mv(
   yi,
   vi, # vi or yield error
   mods = ~ spray_management,
   method = "ML",
   random = ~ 1|trial,
   data = slimmer_PM_dat
)

anova(PM_mv_AI,PM_mv_AI2) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI2)

PM_mv_AI3 <- rma.mv(
   yi,
   vi, # vi or yield error
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ 1 | row_spacing),
   data = slimmer_PM_dat
)

anova(PM_mv_AI2,PM_mv_AI3) # There IS a significant difference between these models, Therefore use the more complicated model with the lower AIC (PM_mv_AI3)

PM_mv_AI4 <- rma.mv(
   yi,
   vi, # vi or yield error
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype),
   data = slimmer_PM_dat
)

anova(PM_mv_AI3,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)

profile(PM_mv_AI4, sigma2 = 1)

PM_mv_AI5 <- rma.mv(
   yi,
   vi, # vi or yield error
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1 | location/year/trial_ref),
   data = slimmer_PM_dat
)

anova(PM_mv_AI4,PM_mv_AI5) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)

summary(PM_mv_AI4)

PM_mv_AI6 <- rma.mv(
   yi,
   vi, # vi or yield error
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ spray_management | D_pres),
   data = slimmer_PM_dat
)

anova(PM_mv_AI6,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)

anova(PM_mv_AI2, PM_mv_AI3)

summary(PM_mv_AI2)

slimmer_PM_dat[is.na(slimmer_PM_dat$AUDPC_m),]
slimmer_PM_dat[slimmer_PM_dat$location == "Emerald", ]
table(slimmer_PM_dat$spray_management)
```
Lets try analysing the data as a risk reduction. 
For this we will use the proportion of yield reductions
```{r}
dat1 <- slimmer_PM_dat[!slimmer_PM_dat$fungicide_ai == "control",]

dat1$yi <- dat1$grain_SMD

PM_mv_MD <- rma.mv(
   yi = yi,
   vi, # vi or yield error
   mods = ~ spray_management - 1,
   method = "ML",
   random = list(~ 1 | location/year , ~1|host_genotype ,~ spray_management|D_pres),
   data = dat1
)

summary(PM_mv_MD)

dat1$D_pres

hist(dat1$grain_SMD)

@@

According to the results of the [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010]. 
However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 2.598; p = 0.0094$). 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 538.26, df = 141, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
meta_cont <- anova(PM_mv_MD, L = rbind(
   c(0, 1, -1, 0, 0,0),
   # early vs Recommended
   c(0, 1, 0, -1, 0,0),
   # early vs recommended plus
   c(0, 1, 0, 0, -1,0),
   # early vs Late 
   c(0, 1, 0, 0, 0,-1),
   # early vs Late plus
   c(0, 0, -1, 1, 0,0),
   # Recommended plus vs recommended
   c(0, 0, -1, 0, 1,0),
   # Late  vs Recommended
   c(0, 0, -1, 0, 0,1),
   # Late_plus  vs Recommended
   c(0, 0, 0, -1, 1,0),
   # Late vs Recommended plus
   c(0, 0, 0, -1, 0,1),
   # Late_plus  vs Recommended plus
   c(0, 0, 0, 0, -1,1)
)) # Late vs Late_plus

@@

data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
      estimates = meta_cont$Lb,
      se = meta_cont$se,
      z_val = meta_cont$zval,
      pval = meta_cont$pval)
```
Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields. Also the model was almost significant when assessing `Late_plus` as saving more yield than `Recommended`. This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
Let's view these comparisons in a plot.

First we will format the results into a data frame and back-transform the log values by using the exponent function
```{r metafor_results}
results_AI <- data.frame(cbind(exp(PM_mv_AI$b),
                               exp((PM_mv_AI$ci.lb)),
                               exp(PM_mv_AI$ci.ub)))

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(
      c(
         "control",
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   )

efficacy$se <- PM_mv_AI$se
colnames(efficacy) <-
   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
efficacy
```

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = c(0.8, 1, 1.2, 1.4),
      color = "grey80",
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

Let's look at how well each of the number treatments compare to each other. We can use the netmeta package to give a graphical representation of this.

@@

```{r netmeta-analysis}
datPM3 <- slimmer_PM_dat %>%
   group_by(trial, spray_management, n) %>%
   summarize(yi_mean = mean(yi),
             vi_mean = mean(vi)) %>%
   ungroup()

>>>>

```{r remove_studies}
#slimmer_PM_dat <-
  # slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),]
```

@@

```{r MSE_2_SVar, eval=FALSE, include=FALSE}
#calculation when using log of response
slimmer_PM_dat$vi <-
   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
                                  2)

@@

   # First we need to Calculate the pooled standard deviation
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <- 
   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yield_error"])/
           (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))

@@

Lets undertake the meta-analysis, we are using the `spray_management` variable as a moderator and a interactive term to the `trial` variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
```{r Metafor-analysis}
dat1$vi <- dat1$yield_error

PM_mv <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management -1,
   method = "ML",
   random = ~ spray_management|trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 7.32, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010]. 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 40994.51, df = 105, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

@@

PM_mv_St <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1|trial),
   data = dat1
)

AIC(PM_mv_St)
anova(PM_mv, PM_mv_St)
```
The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model.

@@

@@

### Profile plots  
Lets inspect the profile plots to ensure the model is not over-fitted. 
We expect to see the estimate align with the peak of the curve. 
Also that the shape of the line is a curve.

```{r}
profile(PM_mv , tau2 = 1)
profile(PM_mv , tau2 = 2)
profile(PM_mv , tau2 = 3)
profile(PM_mv , tau2 = 4)
profile(PM_mv , tau2 = 5)
```

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
meta_cont <- anova(PM_mv, L = rbind(
   c(-1, 1, 0, 0,0),
   c(-1, 0, 1, 0,0),
   c(-1, 0, 0, 1,0),
   c(-1, 0, 0, 0,1),
   c(0, -1, 1, 0,0),
   c(0, -1, 0, 1,0),
   c(0, -1, 0, 0,1),
   c(0, 0, -1, 1,0),
   c(0, 0, -1, 0,1),
   c(0, 0, 0, -1,1)
   ))

@@

source("R/p_star.R")

data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
      estimates = meta_cont$Lb,
      se = meta_cont$se,
      z_val = meta_cont$zval,
      pval = meta_cont$pval,
      VisP = p_star(meta_cont$pval))
```
Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
`Late_plus` is estimated as saving the most yield compared and is significantly higher than all other treatments except `recommended_plus`.  
Let's view these comparisons in a plot.

First we will format the results into a data frame.
```{r metafor_results}
results_AI <- data.frame(cbind(PM_mv$b,
                               PM_mv$ci.lb,
                               PM_mv$ci.ub))

efficacy <- tbl_df(results_AI)
efficacy$Treatment <-
   factor(
      c( "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   )

efficacy$se <- PM_mv$se
colnames(efficacy) <-
   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
efficacy
```

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5,1.5, by = 0.2),
      color = "grey80",
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

Let's look at how well each of the number treatments compare to each other.

We can use the netmeta package to give a graphical representation of the pairwise comparisons.

@@

```{r netmeta-analysis}
datPM3 <- slimmer_PM_dat %>%
   group_by(trial, spray_management, n) %>%
   summarize(yi_mean = mean(grain_SMD),
             vi_mean = mean(yield_error)) %>%
   ungroup()
